Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-07-30 paper/amia.tex
Auto Update from local Sharelatex

Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariable relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}). However, no pipeline currently exists with which computational investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing. This work addresses that gap.

@@

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.

>>>>

Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariate relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}). However, no pipeline currently exists with which computational investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing. This work addresses that gap.

@@

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process. Also included in our GitHub repository are unit tests for KFP using the Python library pytest. Unit tests helped to validate correct functioning of KFP and provides a foundation from which to prevent regressions as new features are added.
